Design of Adaptive Constellations and Error Protection Coding for Wireless Network Coding in 5-node Butterfly Networks

### 2017-05-30 response_letter/response_letter.tex

\def\date#1{\def\@date{#1}}
\def\version#1{\def\@version{#1}}
\def\author#1{\def\@author{#1}}
\def\title#1{\def\@title{#1}}
\def\assignment#1{\def\@assignment{{\it #1}}}
\newcommand{\var}{\rm{var}}

\newcommand{\unfootnote}[1]{
  \renewcommand{\@makefnmark}{}
  \footnotetext{#1}
  \renewcommand{\@makefnmark}{\mbox{$^{\@thefnmark}$}}
}

% \papertitle[title of the paper][Author(s)][Conference type][date + place] 
%\graphicspath{{fig/}}

\begin{document}
\title{Response Letter for EURASIP Journal on Wireless Communications and Networking 
JWCN-D-17-00004 \vskip 1ex
Design of Adaptive Constellations and Error Protection Coding for
Wireless Network Coding in 5-node Butterfly Networks}
\author{Pavel Prochazka, Tomas Uricar, David Halls and Jan Sykora}
\date{\today}
\maketitle
\newpage

We would like to thank all the reviewers for their valuable comments and suggestions. We first reply
to the most common and important questions and then we answer the individual questions and comments
individually.

\section{Common Questions and Corresponding Answers}
\begin{itemize}
  \item CQ1: \emph{Lacking novelty compared to \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}.}
  \item A1: Compared with the conference version \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}, the major contributions and differences of this submitted manuscript are summarized as follows:
  \begin{enumerate} 
  \item We introduce additional performance analysis results for constellations in an uncoded system and an in-depth discussion of the observed results.
  \item We extend the section dealing with the adaptive constellation design in an uncoded system and we supplement additional HW evaluation results for the adaptive system in the whole range of observed channel SNRs. Again a close agreement between between the analytic and measurement results is shown.
  \item We show how the channel coding can be integrated into the proposed constellation design, including the cut-set bound analysis of proper source transmission rates, which provides a hint for the setup of all channel encoders' rates in the system.
  \item We evaluate numerically the performance of the resulting adaptive modulation-coding scheme
  for a wide range of channel conditions in the WBN and we emphasise the performance gains with
    respect to the uncoded system.
  \item We perform a simple robustness analysis, demonstrating that the proposed modulation and coding strategy is viable even in the case when the real world condition induce some deviations from the mathematical system model assumed in the paper.
  \item We conducted a comparison with the state of the art reference scenarios (traditional network
  coding and routing) for the proposed channel coded adaptive constellation design.
  \end{enumerate}
\end{itemize}

\begin{itemize}
  \item CQ2: \emph{Better reference scenario.}
  \item A2: We definitely agree that the zero throughput uncoded QPSK reference scenario is not a very good
  to demonstrate the performance gain of the proposed constellation design. 
  Although, the 2-step scenario does not offer other state of the art solution, we
  decided to consider a comparison with traditional network coding and routing strategies. These
  strategies require 3 steps and therefore some attention is required to provide a fair comparison
  with the proposed 2-step framework. We added a completely new section 7.4 into the manuscript
  dedicated to this comparison  with the conventional techniques.

  Within this new section, we shown that
  the HW implementation of the proposed adaptive constellation design outperforms the reference
  scenarios even with the relaxed assumption (pre-rotation off). In addition we shown that the
  performance of the proposed framework is even above the corresponding reference theoretical limits.
\end{itemize}

\begin{itemize}
  \item CQ3: \emph{Typos and Formatting Issues}
  \item A3: The manuscript was carefully proofread by native speaker for typos. Regarding the
  formatting issues, we searched and corrected the issues we found. Nevertheless, we should stress
  that the manuscript will be transformed to the EURASIP template prior publishing and there will
  be time for final tuning of these issues.
\end{itemize}

\begin{itemize}
  \item CQ4: \emph{Generalization of the proposed Adaptive Constellation Design}
  \item A4:
\end{itemize}

@@

\subsubsection*{Reviewer 1}
\begin{itemize}
  \item Q: \emph{The weak aspect of this paper is that the current paper is a small variation of a
  previous paper by the authors. The authors should further highlight the difference of this paper.}
  \item A: See A1
\end{itemize}

\begin{itemize}
  \item \emph{The authors should edit the paper more carefully. For example, in Figure 5, the
  references are missing. Please go over the whole the paper and make sure similar issues do not
  exist}
  \item A: See A3
\end{itemize}

\subsubsection*{Reviewer 2}
\begin{itemize}
  \item Q: \emph{Since this work builds upon previous work on the application of wireless network
  coding to the WBN, novelty is slightly lacking}
  \item A: see A1
\end{itemize}

\begin{itemize}
  \item Q: \emph{The proposed scheme appears to be quite specific to the WBN, I wonder if it is
  possible to generalize to other similar networks where linear codes yield a good performance.}
  \item A: See A4.  We should stress that the proposed constellation design covers both
  wireless network coding and processing the signal from multiple stages. Join generalization of
  both techniques in the way we did would be extremely challenging, because of time 
  synchronization, pre-rotation, etc. Also note that our approach is basically a 
  practical instance of a well known
  theoretical principle with application of WNC to approximately equal power levels and
  interference cancellation on significantly different power levels. So that its generalization in
  theoretical level is already known. 
\end{itemize}

@@

\begin{itemize}
  \item Q: \emph{The robustness analysis is important, and the authors have done some simulations on this aspect. However, it would be more appreciated if a hardware experiment can be done on this aspect.}
  \item A: We fully understand and agree that the robustness analysis deserves further deep
      investigation. Nevertheless we provided some basic analysis including the hardware experiment
        within our work (check Figure 17 in manuscript) giving quite promising results. A more detailed investigation is suited rather
        for a standalone work than for this resubmission.
\end{itemize}

\begin{itemize}
  \item Q: \emph{In Fig. 15, the throughput enhancmence for the coding scheme is shown. It is
  interesting to see that the throughput enhancment has some "peak" and "valley" as the γ\_MAC
  increases. If possible, please give some explanation. Or this is just a random instance that
  happens to be shown by the hardware experiment, that is also fine.}
  \item A: The explanation here is quite straightforward, as it follows from the steep
  gradients of the uncoded throughput as function of SNRs shown in Figure 10. On the other hand the
  coded throughput as a function of SNRs is much smoother (Figure 14) and therefore their difference
  induces peeks and valleys
\end{itemize}

\begin{itemize}
  \item Q: \emph{There are also some minor context error or typos found}
  \item A: See A3
\end{itemize}

\section{Major Changes Summary}
\begin{itemize}
  \item New section 7.4 containing a more advanced comparison of the proposed framework with the
  state of the art strategies.
  \item Redrawn Figures (see changes in Figures \ref{Fig:Throughput_comparison} and
  \ref{Fig:AchievedRates}).
\end{itemize}
\begin{figure}
    %\begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=0.45\linewidth]{fig/old_Throughput_HSI_XOR_MAC16_BC20_N2.eps}
    \includegraphics[width=0.45\linewidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2.eps}\\
    \includegraphics[width=0.45\linewidth]{fig/old_Throughput_HSI_XOR_MAC20_BC20_N2.eps}
    \includegraphics[width=0.45\linewidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2.eps}\\
    \includegraphics[width=0.45\linewidth]{fig/old_Throughput_HSI_XOR_MAC20_BC16_N2.eps}
    \includegraphics[width=0.45\linewidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2.eps}\\
    \includegraphics[width=0.45\linewidth]{fig/old_Throughput_HSI_XOR_MAC17_BC17_N2.eps}
    \includegraphics[width=0.45\linewidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2.eps}\\
	\caption{Uncoded throughputs (old versions left, new versions right).}
	\label{Fig:Throughput_comparison}
	%\caption{Old uncoded throughput for $\gamma_{\mathrm{MAC}}=16$,$\gamma_{\mathrm{BC}}=20$.}
    %\end{subfigure} 
    %\begin{subfigure}[t]{0.45\textwidth}
    %\caption{New the uncoded throughput for $\gamma_{\mathrm{MAC}}=16$,$\gamma_{\mathrm{BC}}=20$.}
    %\end{subfigure} 
\end{figure}

\begin{figure}
    %\begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=0.45\linewidth]{fig/old_Rate_Regions_XOR_map_BC10_MAC12_HSI8.eps}
    \includegraphics[width=0.45\linewidth]{../fig/Rate_Regions_XOR_map_BC10_MAC12_HSI8.eps}\\
    \includegraphics[width=0.45\linewidth]{fig/old_Rate_Regions_XOR_map_BC5_MAC5_HSI0.eps}
    \includegraphics[width=0.45\linewidth]{../fig/Rate_Regions_XOR_map_BC5_MAC5_HSI0.eps}\\
	\caption{Enlarged fonts -- Figure 13 in the manuscript (old versions left, new versions right).}
	\label{Fig:AchievedRates}
	%\caption{Old uncoded throughput for $\gamma_{\mathrm{MAC}}=16$,$\gamma_{\mathrm{BC}}=20$.}
    %\end{subfigure} 
    %\begin{subfigure}[t]{0.45\textwidth}
    %\caption{New the uncoded throughput for $\gamma_{\mathrm{MAC}}=16$,$\gamma_{\mathrm{BC}}=20$.}
    %\end{subfigure} 
\end{figure}
\bibliographystyle{plain}
\bibliography{bib/Const_design}
\end{document}

### 2017-05-31 Const_design.tex
Few new lines in response letter
Corrected typos

\begin{abstract} % abstract
In this paper we focus on the design of a reliable communication scheme
for generic 5-node Wireless Butterfly Networks (WBN). Since the WBN
represents a natural extension of the basic 2-way relay communication
channel, we follow the paradigm of \emph{Wireless Physical Layer Network
Coding} and we show that the design of novel adaptive constellations\emph{
} is desirable to exploit the promising performance of wireless network coding in WBN.
We introduce a \emph{systematic constellation design} algorithm and
we show that the proposed constellations are capable of outperforming
conventional point-to-point modulations in WBN over the whole range
of channel signal to noise ratios. To further support the applicability of the proposed
constellations in a practical system, we integrate a simple binary
channel coding scheme, providing a robust \emph{adaptive modulation
and coding scheme} for relaying in symmetric WBNs with arbitrary channel
conditions.
\end{abstract}

@@

The invention of Wireless Network Coding\emph{ }(WNC) has indeed provided
a means for a significant enhancement in wireless system performance
\cite{Popovski-Yomo_2007a,Nazer-Gastpar_2011-IEEE-P,Zhang-Liew-Lu_2012}.
However, WNC processing has also revealed several non-trivial research
problems which do not have counterparts in conventional point-to-point
or multi-user systems, like the sensitivity to channel parameterization
\cite{Koike-Popovski-Tarokh_2008,Liu-Tao-Xu_2011-ICC,Yasami-Razi-Abedi_2011,Uricar-Sykora_2011}
or challenging multi-source transmission synchronization \cite{Zhang-Liew-Lam_2006b-ITW,Rosetto-Zorzi_2009-SPAWC,Huang-Wang-Song-Guo-Jamalipour_2012-IEEE-T-WC}.
Furthermore, the specific characteristics of multi-node WNC systems
can call also for novel constellation design approaches (see e.g.
\cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).

In WNC the transmitted information symbols are allowed to interact
directly in the constellation space, inducing a specific set of requirements
on the constellations' properties and characteristics (see e.g. \cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
Generally we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
that any constellation suitable for the specific nature of WNC processing
should be able to form\emph{ a superimposed constellation} with an
appropriate structure at all receiving nodes (allowing direct decoding
of specific WNC functions of user data from the received non-orthogonal
signals \cite{Nazer-Gastpar_2008-ISIT,Sykora-Burr_2011-TVT}) and
simultaneously it should be able to exploit the \emph{broadcast nature
}of wireless channels (allowing a reduction in the consumption of
channel resources in the system \cite{Popovski-Yomo_2007a}). Since
both of these properties hinge on the actual SNR conditions in the
system, the constellation design itself can become a relatively challenging
task.
\begin{figure}
\centering{}
\includegraphics[width=0.6\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_v4}
\caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
\end{figure}

@@

In this paper we extend the communication scheme from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
by appending appropriate \emph{error protection coding} to the system,
resulting in a practical channel-coded adaptive communication scheme
for WBN. We provide the following results and contributions:
\begin{enumerate}
\item We summarize the \emph{systematic constellation design algorithm}
from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC} and we provide
additional numerical results analysing its promising performance.
\item We revise and extend the results discussing the \emph{adaptive capabilities
of the constellations, }including \emph{the constellation mapping
regions} for adaptive WBN relaying\emph{.}
\item We validate the proposed design in a \emph{real-world HW setup}, including
the HW evaluation of adaptive system performance.
\item We show how the \emph{channel coding} can be integrated into the proposed
constellation design, including the analysis of proper source transmission
rates.
\item We evaluate numerically the performance of the resulting \emph{adaptive
modulation and coding} scheme for a wide range of channel conditions
in the WBN.
\item We show that the proposed design is viable even if the real-world
conditions induce some deviation from the assumed system model.
\item We compare the proposed design with state of the art reference scherios to highlight its
superior performance.
\end{enumerate}
The rest of the paper is organized as follows. The system model, including
all necessary definitions and details about WNC processing in WBNs
is summarized in Section~\ref{sec:CTUpp_SystemModel}. A systematic
\emph{constellation design algorithm} for WBNs is revised in Section~\ref{sec:CTUpp_Euclidean-Distance-based-Constel}.
The performance analysis of the proposed constellations (including
the HW evaluation) in an uncoded system is available in Section~\ref{sec:CTUpp_Performance-Analysis-Uncoded}.
Section~\ref{sec:CTUpp_Adaptive-Constellation-Design} discusses
an adaptive constellation design and Section~\ref{sec:CTUpp_Channel-Coding}
introduces the channel coding extension to the system. The performance
of the novel adaptive modulation and coding scheme is analyzed in
Section~\ref{sec:CTUpp_Performance-Analysis-Coded}, including a
simple robustness analyzis. Concluding remarks are summarized in Section~\ref{sec:CTUpp_DiscussionConclusions-etc}.

@@

The coefficients $L_{n}^{b},\,L_{n}^{s}$ (\ref{eq:CTUpp_superpositionModulation})
are generally taken from the set of complex numbers. However, for
the sake of simplicity we limit the scaling coefficients $L_{n}^{b},\,L_{n}^{s}$
to a purely imaginary or real numbers. Even though that this simplified
approach can potentially result in a sub-optimal performance in fading
channels (complex channel coefficients $h_{iR}$, $i\in\{A,B\}$ can
rotate the component superposition constellations), we follow this
simplification to show the basic ideas of the proposed superposition
modulation design. The extension to general complex $L_{n}^{b},\,L_{n}^{s}$
can naturally embrace the source phase pre-rotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which virtually reverts the fading channel to the conventional Additive
White Gaussian Noise (AWGN) channel with $\varangle h_{ij}=0$.

@@

For the sake of simplicity of the theoretical performance analysis,
we assume that source$\rightarrow$relay channels in WBN are AWGN\footnote{Note that this also includes the system with perfect source phase
prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which can be obtained by a generalization of the scaling coefficients
as $L'_{n}=L_{n}e^{-\jj\measuredangle h_{SR}}$, where $h_{SR}$ is
the corresponding source$\rightarrow$relay channel.} (i.e. $h_{iR}=1$ for $i\in\{A,B\}$). We evaluate the throughput
analytically as $(N_{b}+N_{s})\cdot(1-P_{e}^{\mathrm{FER}})$, where
$P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
symmetry we evaluate the throughput of $S_{A}\to D_{A}$ only. We
set the frame length to $M=768$ symbols (to match the HW evaluation)
and the relay output mapper $\mathcal{A}^{R}$ will be defined as
a conventional $(2^{N_{b}+2N_{s}})$-QAM constellation. All performance
metrics in the symmetric WBN are evaluated as a function of the actual
SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}},\,\gamma_{{\rm {BC}}}$).
\begin{figure*}
\centering{}
\includegraphics[width=0.8\textwidth]{fig/d2_1}
\caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
constellations are depicted as blue circles ($S_{A}$ output constellation),
red circles ($S_{B}$ output constellation) and squares (received
superimposed constellation at $R$). Hierarchical function is $f\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$.\label{fig:CTUpp_ConstellationDesignExample} }
\end{figure*}
\begin{figure*}
\begin{centering}
\includegraphics[width=0.95\textwidth]{fig/const_all_2}
\par\end{centering}

@@

A 5-node, 2x1x2 topology with two sources, one relay and two destinations,
is used as shown in Fig. \ref{fig:CTUpp_HW_setup}. The USRPs each
have a single 3dBi omni-directional antenna (at 2.4 - 2.5 GHz and
4.9 - 5.85 GHz). The first source transmitter ($S_A$) USRP is connected
to a powerful Core i7 laptop, running a single instance of GNURadio,
by a Gigabit Ethernet link. The second source transmitter ($S_B$)
USRP is connected to the first by the MIMO expansion cable. This provides
the second transmitter with baseband data from GNURadio as well as
synchronization signals from the first transmitter. The relay, $D_{A}$
and $D_{B}$ USRPs are connected to further laptops running GNURadio
by Gigabit Ethernet links. More details about synchronization, carrier
frequency offset and timing offset estimation can be found in \cite{Hynek-etal_2014-EW}.
In this paper, the MIMO cable is used to synchronize the frequency
of the two source USRPs, as well as to achieve sample-level timing
synchronization. The latter avoids asynchronism in the superimposed
constellations at the relays; more details about the impact of asynchronism
in WNC can be found in \cite{Diwine_D512}. Furthermore an Ettus Octoclock
clock distribution system \cite{Ettus_OctoClock} is used to provide
external frequency synchronization signals to all nodes. This allows
us to show system performance, and compare with the theoretical and
simulation cases, without the impact of asynchronism affecting the
results. Results with additional real-world impairments are a focus
for future work, as discussed in the final section of this paper.
Channel tracking using pilots is implemented as detailed in \cite{Hynek-etal_2014-EW},
however, due to the static indoor environment (used to mimic the AWGN
channel used in the theoretical work as closely as possible) the channel
does not change significantly over the frame duration. The USRPs are
closely located in line-of-sight to ensure the channel between them
is fairly static, without fading, thus mimicking the channel used
in the theoretical work. Moreover as cabled synchronisation is used,
it is desirable to minimize the cable length. Low SNRs are achieved
between the USRPs using low transmit powers.

@@

The SNR mapping regions, including the resulting throughput for the
optimal choice of $N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$, are shown
as a function of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$ for
$\gamma_{{\rm {BC}}}\in\{15\,\mathrm{dB},\,17\,\mathrm{dB},20\,\mathrm{dB},25\,\mathrm{dB}\}$
in Fig.~\ref{fig:CTUpp_SNR_map_BC15-17-20-25}. Several interesting
phenomenas can be again observed in the figure:
\begin{itemize}
\item Since the transmission schemes with ($N_{b}=0,\,N_{s}>0$) constellations
can ignore the HSI channels (Table~\ref{tab:CTUpp_SC-relaying-scheme}),
these constellations are optimal in the low $\gamma_{{\rm {HSI}}}$
region ($\gamma_{{\rm {HSI}}}<8\,\mathrm{dB}$), regardless of the
other channels' SNRs $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The constellations with ($N_{b}>0,\,N_{s}=0$) provide the best performance
in a substantial part of the medium-to-high $\gamma_{{\rm {HSI}}}$
regions, depending on the actual $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The \textquotedbl{}combined\textquotedbl{} constellations ($N_{b}>0,\,N_{s}>0$)
provide the maximal throughput (for sufficiently high $\gamma_{{\rm {BC}}}$)
in relatively large regions of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$
(see the dominant throughput regions of $(N_{b}^{{\rm I}},\,N_{s}^{{\rm I}})=(2,1)$
for $\gamma_{{\rm {BC}}}=\left\{ 20\,\mathrm{dB},\,25\,\mathrm{dB}\right\} $).
Note that these constellations have a great potential for application
in systems with limited or partial HSI (see \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}).
\begin{figure*}
\begin{centering}
\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC15}
\quad
\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC17}
\par\end{centering}

@@

\subsubsection{Reference Three-Step Scenarios}\label{Sec:Reference-3step-models}
In the first scenario both sources transmit their information one by one, but the relay is
allowed to combine the received (fully decoded) data packets into the network coded packet
$f(d_{A},d_{B})=d_{A}\oplus d_{B}$ and HSI channels are necessary to retrieve the desired
information at both sources, that is the traditional network coding approach (see Figure
\ref{fig:CTUpp_ref3stepNC}).

>>>>

\begin{abstract} % abstract
In this paper, we focus on the design of a reliable communication scheme
for generic 5-node Wireless Butterfly Networks (WBN). Since the WBN
represents a natural extension of the basic 2-way relay communication
channel, we follow the paradigm of \emph{Wireless Physical Layer Network
Coding} and we show that the design of novel adaptive constellations
 is desirable to exploit the promising performance of wireless network coding in WBN.
We introduce a \emph{systematic constellation design} algorithm and
we show that the proposed constellations are capable of outperforming
conventional point-to-point modulations in WBN over the whole range
of channel signal to noise ratios. To further support the applicability of the proposed
constellations in a practical system, we integrate a simple binary
channel coding scheme, providing a robust \emph{adaptive modulation
and coding scheme} for relaying in symmetric WBNs with arbitrary channel
conditions.
\end{abstract}

@@

The invention of Wireless Network Coding\emph{ }(WNC) has provided
a means for a significant enhancement in wireless system performance
\cite{Popovski-Yomo_2007a,Nazer-Gastpar_2011-IEEE-P,Zhang-Liew-Lu_2012}.
However, WNC processing has also revealed several non-trivial research
problems which do not have counterparts in conventional point-to-point
or multi-user systems, like the sensitivity to channel parameterization
\cite{Koike-Popovski-Tarokh_2008,Liu-Tao-Xu_2011-ICC,Yasami-Razi-Abedi_2011,Uricar-Sykora_2011}
or challenging multi-source transmission synchronization \cite{Zhang-Liew-Lam_2006b-ITW,Rosetto-Zorzi_2009-SPAWC,Huang-Wang-Song-Guo-Jamalipour_2012-IEEE-T-WC}.
Furthermore, the specific characteristics of multi-node WNC systems
can call also for novel constellation design approaches (see e.g.
\cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).

In WNC the transmitted information symbols are allowed to interact
directly in the constellation space, inducing a specific set of requirements
on the constellations' properties and characteristics (see e.g. \cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
Generally, we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
that any constellation suitable for the specific nature of WNC processing
should be able to form\emph{ a superimposed constellation} with an
appropriate structure at all receiving nodes (allowing direct decoding
of specific WNC functions of user data from the received non-orthogonal
signals \cite{Nazer-Gastpar_2008-ISIT,Sykora-Burr_2011-TVT}) and
simultaneously it should be able to exploit the \emph{broadcast nature
}of wireless channels (allowing a reduction in the consumption of
channel resources in the system \cite{Popovski-Yomo_2007a}). Since
both of these properties hinge on the actual SNR conditions in the
system, the constellation design itself can become a relatively challenging
task.
\begin{figure}
\centering{}
\includegraphics[width=0.6\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_v4}
\caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
\end{figure}

@@

In this paper, we extend the communication scheme from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
by appending appropriate \emph{error protection coding} to the system,
resulting in a practical channel-coded adaptive communication scheme
for WBN. We provide the following results and contributions:
\begin{enumerate}
\item We summarize the \emph{systematic constellation design algorithm}
from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC} and we provide
additional numerical results analysing its promising performance.
\item We revise and extend the results discussing the \emph{adaptive capabilities
of the constellations, }including \emph{the constellation mapping
regions} for adaptive WBN relaying\emph{.}
\item We validate the proposed design in a \emph{real-world hardware (HW) setup}, including
the HW evaluation of adaptive system performance.
\item We show how the \emph{channel coding} can be integrated into the proposed
constellation design, including the analysis of proper source transmission
rates.
\item We evaluate numerically the performance of the resulting \emph{adaptive
modulation and coding} scheme for a wide range of channel conditions
in the WBN.
\item We show that the proposed design is viable even if the real-world
conditions induce some deviation from the assumed system model.
\item We compare the proposed design with state of the art reference scenarios to highlight its
superior performance.
\end{enumerate}
The rest of the paper is organized as follows. The system model, including
all necessary definitions and details about WNC processing in WBNs
is summarized in Section~\ref{sec:CTUpp_SystemModel}. A systematic
\emph{constellation design algorithm} for WBNs is revised in Section~\ref{sec:CTUpp_Euclidean-Distance-based-Constel}.
The performance analysis of the proposed constellations (including
the HW evaluation) in an uncoded system is available in Section~\ref{sec:CTUpp_Performance-Analysis-Uncoded}.
Section~\ref{sec:CTUpp_Adaptive-Constellation-Design} discusses
an adaptive constellation design and Section~\ref{sec:CTUpp_Channel-Coding}
introduces the channel coding extension to the system. The performance
of the novel adaptive modulation and coding scheme is analyzed in
Section~\ref{sec:CTUpp_Performance-Analysis-Coded}, including a
simple robustness analysis. Concluding remarks are presented in Section~\ref{sec:CTUpp_DiscussionConclusions-etc}.

@@

The coefficients $L_{n}^{b},\,L_{n}^{s}$ (\ref{eq:CTUpp_superpositionModulation})
are generally taken from the set of complex numbers. However, for
the sake of simplicity, we limit the scaling coefficients $L_{n}^{b},\,L_{n}^{s}$
to purely imaginary or real numbers. Even though this simplified
approach can potentially result in a sub-optimal performance in fading
channels (complex channel coefficients $h_{iR}$, $i\in\{A,B\}$ can
rotate the component superposition constellations), we follow this
simplification to show the basic ideas of the proposed superposition
modulation design. The extension to general complex $L_{n}^{b},\,L_{n}^{s}$
can naturally embrace the source phase pre-rotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which virtually reverts the fading channel to the conventional Additive
White Gaussian Noise (AWGN) channel with $\varangle h_{ij}=0$.

@@

For the sake of simplicity of the theoretical performance analysis,
we assume that source$\rightarrow$relay channels in WBN are AWGN\footnote{Note that this also includes the system with perfect source phase
prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which can be obtained by a generalization of the scaling coefficients
as $L'_{n}=L_{n}e^{-\jj\measuredangle h_{SR}}$, where $h_{SR}$ is
the corresponding source$\rightarrow$relay channel.} (i.e. $h_{iR}=1$ for $i\in\{A,B\}$). We evaluate the throughput
analytically as $(N_{b}+N_{s})\cdot(1-P_{e}^{\mathrm{FER}})$, where
$P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
symmetry, we evaluate the throughput of $S_{A}\to D_{A}$ only. We
set the frame length to $M=768$ symbols (to match the HW evaluation)
and the relay output mapper $\mathcal{A}^{R}$ will be defined as
a conventional $(2^{N_{b}+2N_{s}})$-QAM constellation. All performance
metrics in the symmetric WBN are evaluated as a function of the actual
SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}},\,\gamma_{{\rm {BC}}}$).
\begin{figure*}
\centering{}
\includegraphics[width=0.8\textwidth]{fig/d2_1}
\caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
constellations are depicted as blue circles ($S_{A}$ output constellation),
red circles ($S_{B}$ output constellation) and squares (received
superimposed constellation at $R$). Hierarchical function is $f\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$.\label{fig:CTUpp_ConstellationDesignExample} }
\end{figure*}
\begin{figure*}
\begin{centering}
\includegraphics[width=0.95\textwidth]{fig/const_all_2}
\par\end{centering}

@@

A 5-node, 2x1x2 topology with two sources, one relay and two destinations,
is used as shown in Fig. \ref{fig:CTUpp_HW_setup}. The USRPs each
have a single 3dBi omni-directional antenna (at 2.4 - 2.5 GHz and
4.9 - 5.85 GHz). The first source transmitter ($S_A$) USRP is connected
to a powerful Core i7 laptop, running a single instance of GNURadio,
by a Gigabit Ethernet link. The second source transmitter ($S_B$)
USRP is connected to the first by the MIMO expansion cable. This provides
the second transmitter with baseband data from GNURadio as well as
synchronization signals from the first transmitter. The relay, $D_{A}$
and $D_{B}$ USRPs are connected to further laptops running GNURadio
by Gigabit Ethernet links. More details about synchronization, carrier
frequency offset and timing offset estimation can be found in \cite{Hynek-etal_2014-EW}.
In this paper, the MIMO cable is used to synchronize the frequency
of the two source USRPs, as well as to achieve sample-level timing
synchronization. The latter avoids asynchronism in the superimposed
constellations at the relays; more details about the impact of asynchronism
in WNC can be found in \cite{Diwine_D512}. Furthermore, an Ettus Octoclock
clock distribution system \cite{Ettus_OctoClock} is used to provide
external frequency synchronization signals to all nodes. This allows
us to show system performance, and compare with the theoretical and
simulation cases, without the impact of asynchronism affecting the
results. Results with additional real-world impairments are a focus
for future work, as discussed in the final section of this paper.
Channel tracking using pilots is implemented as detailed in \cite{Hynek-etal_2014-EW},
however, due to the static indoor environment (used to mimic the AWGN
channel used in the theoretical work as closely as possible) the channel
does not change significantly over the frame duration. The USRPs are
closely located in line-of-sight to ensure the channel between them
is fairly static, without fading, thus mimicking the channel used
in the theoretical work. Moreover, as cabled synchronisation is used,
it is desirable to minimize the cable length. Low SNRs are achieved
between the USRPs using low transmit powers.

@@

The SNR mapping regions, including the resulting throughput for the
optimal choice of $N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$, are shown
as a function of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$ for
$\gamma_{{\rm {BC}}}\in\{15\,\mathrm{dB},\,17\,\mathrm{dB},20\,\mathrm{dB},25\,\mathrm{dB}\}$
in Fig.~\ref{fig:CTUpp_SNR_map_BC15-17-20-25}. Several interesting
phenomena can be again observed in the figure:
\begin{itemize}
\item Since the transmission schemes with ($N_{b}=0,\,N_{s}>0$) constellations
can ignore the HSI channels (Table~\ref{tab:CTUpp_SC-relaying-scheme}),
these constellations are optimal in the low $\gamma_{{\rm {HSI}}}$
region ($\gamma_{{\rm {HSI}}}<8\,\mathrm{dB}$), regardless of the
other channels' SNRs $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The constellations with ($N_{b}>0,\,N_{s}=0$) provide the best performance
in a substantial part of the medium-to-high $\gamma_{{\rm {HSI}}}$
regions, depending on the actual $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The \textquotedbl{}combined\textquotedbl{} constellations ($N_{b}>0,\,N_{s}>0$)
provide the maximal throughput (for sufficiently high $\gamma_{{\rm {BC}}}$)
in relatively large regions of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$
(see the dominant throughput regions of $(N_{b}^{{\rm I}},\,N_{s}^{{\rm I}})=(2,1)$
for $\gamma_{{\rm {BC}}}=\left\{ 20\,\mathrm{dB},\,25\,\mathrm{dB}\right\} $).
Note that these constellations have a great potential for application
in systems with limited or partial HSI (see \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}).
\begin{figure*}
\begin{centering}
\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC15}
\quad
\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC17}
\par\end{centering}

@@

\subsubsection{Reference Three-Step Scenarios}\label{Sec:Reference-3step-models}
In the first scenario both sources transmit their information one by one, but the relay is
allowed to combine the received (fully decoded) data packets into the network coded packet
$f(d_{A},d_{B})=d_{A}\oplus d_{B}$ and HSI channels are necessary to retrieve the desired
information at both sources. This is the traditional network coding approach (see Figure
\ref{fig:CTUpp_ref3stepNC}).

The second scenario is equivalent to conventional routing, where the sources subsequently transmit
their data packet towards the relay. The relay then sends complete source information (no NC coding is
applied) and thus the HSI channels are completely ignored (see Figure \ref{fig:CTUpp_ref3stepRouting}).
